---
title: "Energy Efficiency"
output: 
    flexdashboard::flex_dashboard:
        orientation: columns
        vertical_layout: fill
        self_contained: true
        social : ["twitter","facebook","menu"]
        source_code : embed
runtime: shiny
---


```{r load-packages, cache=TRUE}
library(tidyverse)
library(readxl)
library(ggplot2)
library(psych)
library(reshape2)
library(clusterSim) #normalization
library(cowplot)


```


```{r load-data, cache=TRUE}
df <- read_excel('./ENB2012_data.xlsx')
#create a vector of the columns
df_column <- c('Relative_Compactness','Surface_Area', 'Wall_Area','Roof_Area','Overall_Height','Orientation','Glazing_Area','Glazing_Area_Distribution','Heating_Load','Cooling_Load')

colnames(df) <- df_column

```

# Energy Prediction
## controls {.sidebar}

```{r file-input}

fileInput(
  inputId = 'fileupload',
  label = 'Please upload an excel file',
  multiple = FALSE,
  buttonLabel = 'Upload',
  placeholder = 'waiting for file'
)


```


```{r data-upload}
#create a vector of the columns
df_column <- c('Relative_Compactness','Surface_Area', 'Wall_Area','Roof_Area','Overall_Height','Orientation','Glazing_Area','Glazing_Area_Distribution','Heating_Load','Cooling_Load')

theData <- reactive({
   if(is.null(input$fileupload)) {
     return(NULL)
   }
  read_excel(input$fileupload$datapath)

})

```



```{r column-selected}


df_select <- reactive(checkboxGroupInput(
  inputId = 'colselect',
  label = 'Select Required Columns',
  choices = names(theData())
))

renderUI(df_select())
```



## Data View {.tabset}

### Data View
```{r}

DT::renderDataTable(DT::datatable(theData()))

```




# Description
## page1-col1 {.tabset}

### Table
```{r display-table}
#DT::renderDataTable(DT::datatable(df))
DT::datatable(df)
```

###Corelation Plot
```{r pair-plots}

renderPlot(pairs.panels(df[,-c(9,10)]))

```



### Histogram

```{r hist-var}
selectInput(
  inputId = 'HistVar',
  label = 'Please Select a column',
  choices = names(df)
)

```

The histogram for the selected column is shown below


```{r histogtam}
renderPlot(ggplot(df, aes_string(x=input$HistVar)) + geom_histogram() + theme_classic())
```


# Random Forest
##page2-col1
### Model Summary : Heating
```{r model}
library(randomForest)

#split datasets input features and target

M1 <- df[,-10]  #heating
m2 <- df[,-9] #cooling
```

```{r train-model}
rf_heating <- randomForest(Heating_Load ~ ., data = M1, mtry=3, importance = TRUE, na.action = na.omit)

renderPrint(rf_heating)
```



### Model Summary : Cooling
```{r cooling-model}
rf_cooling <- randomForest(Cooling_Load ~ ., data = m2, mtry=3, importance = TRUE, na.action = na.omit)

renderPrint(rf_cooling)

```


##page2-col2
### Feature Importance : Heating
```{r heating-features}
renderPrint(rf_heating$importance)

```


### Feature Importance : Cooling

```{r cooling-features}
renderPrint(rf_cooling$importance)

```


# Linear Model
## Heating {.tabset}
### Summary Linear Model : Heating
```{r lm-heating}
lm_heating <- lm(Heating_Load ~.,data = M1)

renderPrint(summary(lm_heating))

```

### ANOVA : Heating
```{r anova-heating}
renderPrint(anova(lm_heating))

```


### Summary Linear Model : Cooling
```{r}
lm_cooling <- lm(Cooling_Load ~ ., data = m2)
renderPrint(summary(lm_cooling))

```


### ANOVA : Cooling
```{r anova-cooling}
renderPrint(anova(lm_cooling))
```





